Memo: MWA beam-correction formulae

### 2013-08-20 articles/Report-MWA-Beam/mwa-beam.tex
Adding Jones notation

Eq.~\ref{apply-beam-image-space} describes how to apply the beam to a single measurement. The RTS integrates multiple snapshots with different beam values, which requires a weighted average of the measurements. A measurement is beam-corrected and weighted by the square of the beam value. These weighted measurements are summed together and finally the total weight is divided out. Therefore, the final pixel value $\mathbf{s'}$ is estimated from the individual measurements $\mathbf{v}_i$ and their corresponding beam values $\mathbf{B}_i$ as:
\begin{equation}
\mathbf{s'} = \left( \sum\limits_{i=1}^N \textbf{W}_i \mathbf{s}_i \right) \left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{equation}
with
\begin{equation}
\textbf{W}_i = \mathbf{T} \left[ \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)\right].
\end{equation}
In this, $\mathbf{s}_i$ can be substituted with Eq.~\ref{apply-beam-image-space} to prevent having to invert the beam for every measurement:
\begin{equation}
\mathbf{s'} = 
\left(
  \sum\limits_{i=1}^N \mathbf{T} \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right) 
  \mathbf{T} \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^{-1} \mathbf{v}
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{equation}
\{ We can weight first and calculates Stokes parameters later \}
\begin{eqnarray}
\notag
\mathbf{s'} & =  &
\left(
  \mathbf{T} \sum\limits_{i=1}^N \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right) 
  \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^{-1} \mathbf{v}
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1} \\
& = &
\left(
  \mathbf{T} \sum\limits_{i=1}^N \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \mathbf{v}
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{eqnarray}

>>>>

Eq.~\ref{apply-beam-image-space} describes how to apply the beam to a single measurement. The RTS integrates multiple snapshots with different beam values, which requires a weighted average of the measurements. A measurement is beam-corrected and weighted by the square of the beam value. These weighted measurements are summed together and finally the total weight is divided out. Therefore, the final pixel value $\mathbf{s'}$ is estimated from the individual measurements $\mathbf{s}_i$ and their corresponding beam values $\mathbf{B}_i$ as:
\begin{equation} \label{eq:weighting}
\mathbf{s'} = \left( \sum\limits_{i=1}^N \textbf{W}_i \mathbf{s}_i \right) \left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{equation}
with
\begin{equation} \label{eq:weight-per-value}
\textbf{W}_i = \mathbf{T} \left[ \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)\right].
\end{equation}
In this, $\mathbf{s}_i$ can be substituted with Eq.~\ref{apply-beam-image-space} to prevent having to invert the beam for every measurement:
\begin{equation}
\mathbf{s'} = 
\left(
  \sum\limits_{i=1}^N \mathbf{T} \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right) 
  \mathbf{T} \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^{-1} \mathbf{v}_i
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{equation}
\{ We can weight first and calculates Stokes parameters later \}
\begin{eqnarray}
\notag
\mathbf{s'} & =  &
\left(
  \mathbf{T} \sum\limits_{i=1}^N \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right) 
  \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^{-1} \mathbf{v}_i
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1} \\
\label{eq:weighting-final}
& = &
\left(
  \mathbf{T} \sum\limits_{i=1}^N \left(\mathbf{B}_i \otimes \mathbf{B}_i^{*T} \right)^* \mathbf{v}_i
\right)
\left( \sum\limits_{i=1}^N \textbf{W}_i \right)^{-1},
\end{eqnarray}
\section{Using Jones matrices}
Because our optical system is 'pure', the Mueller $4\times 4$-matrix calcules can be avoided by using $2\times 2$ Jones matrices. The relationship between these two is:
\begin{equation}
\left(\mathbf{A} \otimes \mathbf{B}^{*T}\right) \mathbf{v} = \textbf{AVB}^*.
\end{equation}
The left hand side multiplies a $4\times 4$ matrix with a vector containing the visibilities ordered as $\mathbf{v}=[v_{xx}, v_{xy}, v_{yx}, v_{yy}]^T$, while the right hand side uses the $2\times 2$ matrix
\begin{equation}
\mathbf{V}=\left(\begin{array}{cc}
v_{xx} & v_{xy}\\ v_{yx} & v_{yy}
\end{array}\right).
\end{equation}
Using this relation, Eq.~\eqref{eq:weighting-final}, excluding conversion to Stokes, can be rewritten:
\begin{eqnarray}
\mathbf{R}=
\left( \sum\limits_{i=1}^N \mathbf{B}^*\mathbf{B}\right)^{-1}
\left( \sum\limits_{i=1}^N \mathbf{B}^*\mathbf{V}\mathbf{B} \right)
\left( \sum\limits_{i=1}^N\mathbf{B}^*\mathbf{B}\right)^{-1}
\end{eqnarray}
